Efficient Computation of Extended Sources

### 2021-05-18 repro/papers/sseprecond/paper.tex
interim

Discretization is conventional, with a rectangular grid and staggered
finite difference scheme \cite[]{Virieux:84} of order 2 in time and
2$k$ in space; for most of the experiments reported below, $k=4$.
Sampling operators such as $P_r$ are implemented via linear
interpolation, and source insertion via adjoint linear interpolation
(as noted above, in the continuum limit, sources are represented via
adjoint sampling). Steps in $x$ and $z$ are the same. Most results use
$\Delta x = 20$ m, and limit the temporal frequency of the computed
traces to 12.5 Hz. We also explore the dependence of a few results on frequency, using
$\Delta x = 10$ m and $5$ m, to accomodate 25 and 50 Hz respectively,
maintaining 8 samples per wavelength.

@@

>>>>

Discretization is conventional, with a rectangular grid and staggered
finite difference scheme \cite[]{Virieux:84} of order 2 in time and
2$k$ in space; for most of the experiments reported below, $k=4$.
Sampling operators such as $P_r$ are implemented via linear
interpolation, and source insertion via adjoint linear interpolation
(as noted above, in the continuum limit, sources are represented via
adjoint sampling). Steps in $x$ and $z$ are the same. Most results use
$\Delta x = 20$ m, and limit the temporal frequency of the computed
traces to 12.5 Hz. We also explore the dependence of a few results on frequency, using
$\Delta x = 10$ m and $5$ m, to accomodate 25 and 50 Hz respectively,
maintaining 8 samples per wavelength. All computations are carried out
in single precision.

\cite{GeoPros:11} gives a description of the code
implementation, out-of-date in a few respects but overall accurate.

@@

The implemented code uses the adjoint state method on the discrete
level, to assure that the computed adjoint operators are adjoint at
the level of machine precision to the computed operators. The issue of
reverse-time storage is resolved through the optimal checkpointing
technique \cite[]{Griewank:book,Symes:06a-pub}, again without loss of
precision.

Typical results with pseudorandom input traces $d_r, h_z, w_r, f_s$ are:
\begin{itemize}
\item computed $\langle d_r, S^+_{z_s,z_r}h_s\rangle = -2.41069174,
  \langle (S^+_{z_s,z_r})^Td_r, h_s \rangle = -2.41069388.$
\item  computed $\langle w_r, V^+_{z_s,z_r}f_s\rangle = -2.73362470,
  \langle (V^+_{z_s,z_r})^Tw_r, f_s \rangle = -2.73362136.$
\end{itemize}
Ideally, the differences of these inner products should be at most a
relatively small multiple of machine precision, {\em relative} to the
products $\|d_r\|\| S^+_{z_s,z_r}\|\|h_s\|$ and
$\|w_r\|\|V^+_{z_s,z_r}\|\|f_s\|$ (thus making the result
dimensionless). The operator norm $\| S^+_{z_s,z_r}\|$ is
computationally inaccessible, so instead I used the smaller quantities
$\|d_r\|\| S^+_{z_s,z_r}h_s\|$ etc. as stand-ins - thereby
overestimating the relative error between the inner products. In all
cases, over a very large number of random inputs, the largest observed
relative error estimate was $O(10^{-9}$, well under the appropriate limit for
single precision.

\section{Approximate Inversion}

\section{Iterative Inversion}
